---
title: "Assignemnt 4.2: Framing Ready for 100"
author: "Bri Baker, Craig Kopulsky, Lauren Skube"
date: "1/27/2021"
output: html_document
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr) #for data wrangling
library(readxl) #for reading Excel file
library(tidyverse) #for dataframe functions
library(janitor) #for renaming variables
library(ggplot2) #for plotting
library(stringr) #for text manipulation

`%nin%` = Negate(`%in%`)
```

## Introduction

To progress the *Ready for 100* policy campaign, we need to identify and sway potential key players in the legislature. Herein we outline our code and reasoning for the identification of a member of congress whose vote margins, League of Conservation Voters (LCV) score, and district preferences make their district an ideal choice for a public campaign pushing *Ready for 100*. 

We identified District 6 of Florida as a key public audience for our campaign. 


## Process


### Data

The dataset utilized includes: politicians elected to the U.S. House of Representatives in 2018, constituent opinion in their districts on a variety of measures, and their LCV score in 2019.

```{r data, message=FALSE}

data <- read_csv("congress_116_data.csv") # 116th congress data
metadata <- read_csv("Combined_Metadata.csv") # metadata for "data"

#reordering metadata 'variable' to match variable order in 'data':
order <- match(names(data),metadata$variable)
metadata <- metadata[order,]

```

### Primary and general election vulnerability

Congresspeople who are likely to be receptive to pressure about policy change from their constituencies are those in districts with narrow vote margins, so we first identified the vulnerable House members. We did this by filtering the dataset to include members whose vote margin was less than 0.6 in either the primary or the general election.

```{r vulnerable, fig.cap="Figure 1. Congressional Districts with Vote Percentages of 60% or less in 2018 House Primary or General Elections"}

#selecting for vulnerable House members:
vulnerable <- data %>%
  filter(primary_percent < 0.6 | general_percent < 0.6)

#plotting the distribution of primary and general margins:
group.colors <- c(D = "blue", R = "red", IDP ="green")
ggplot(vulnerable, aes(x = primary_percent, 
                       y = general_percent,
                       color = party)) + 
  geom_point() +
  geom_text(aes(label = district_id),
            hjust = 0, vjust = 0) +
  scale_color_manual(values = group.colors) + 
  labs(x = "Primary Election Votes (%)",
       y = "General Election Votes (%)")


```

```{r lcv, fig.cap= "Figure 2. LCV Scores of Representatives from Congressional Districts with Vote Percentages of 60% or less in 2018 House Primary or General Elections"}

lcv_vulnerable <- vulnerable %>% 
  select(lcv_score, party) 

ggplot(lcv_vulnerable, aes(x = party, y = lcv_score)) +
  geom_jitter()
```


Both Democratic and Republican congresspeople are vulnerable in their upcoming reelection (Figure 1). To ensure that *Ready for 100* policy progresses, it is important to ensure that districts that leaned Democratic in 2018 (and therefore chose representatives with generally higher LCV scores) stay that way in the upcoming election. However, there are many Republican-leaning districts along the vulnerable margin where the representatives have high to mid-level LCV scores (Figure 2).

## Target district determinination

We intend to target a district with a vulnerable mid-level LCV representative whose constituency has a high percentage of people who are on on some level concerned about the impacts of climate change and interested in funding renewables.

With that in mind, we filtered Republican representatives by primary vulnerability (<0.6) and LCV score (<55) to find districts with high primary vulnerability and low LCV scores. We then plotted those individuals against the proportions of their constituencies that support the funding of renewable energy research and development.


```{r district choice, fig.cap="Figure 3. LCV Scores of vulnerable Republicans with LCV scores less than 55 compared to proportion of constituents that want to fund renewables."}
#selecting republicans vulnerable to primary challenges who are not strongest possible environmentalists:
vulnerableR <- data %>%
  filter(primary_percent < 0.6 & party == "R" & lcv_score<55)

#plotting the distribution of LCV scores vs. constituent support to address climate:
ggplot(vulnerableR, aes(x= lcv_score, 
                       y= fundrenewables)) + 
  geom_point() +
  geom_text(aes(label=district_id),
            hjust=0, vjust=0) +
  labs(x = "LCV score",
       y = "Percent of constituency (%)") +
  xlim(c(0,40))

```
```{r, echo=FALSE}
FL06 <- vulnerableR %>% 
  filter(district_id =="FL 06")
```



From this analysis, we identified District 06 in Florida as a likely district where the opinions of the constituency could sway policy decisions regarding *Ready for 100* of their vulnerable representative (Figure 3). This is because constituents in this district have high support for renewables (`r round(FL06$fundrenewables, 2)`%) and the representative Michael Waltz, has an LCV score closer to 50 than representatives in other constituencies (LCV = `r FL06$lcv_score`). In the 2018 election Michael Waltz won `r round(100*FL06$primary_percent, 2)`% of the vote in the primary and `r round(100*FL06$general_percent, 2)`% in the general election which indicates that he is vulnerable to pressure from his constituency.


## Key Public Audience

Southern st johns, flagler, volusia and eastern lake county
84% White
$43,375 median income
unemployment 11%
67% of folks think harm to future generations
54% climate change human caused

economic and personal rights for clean env for you and your kids framing


Congressional district 06, which includes Southern St. Johns, Flagler, Volusia, and Eastern Lake County is about 40% Republican and about 32% Democrat by voter registration. While Biden won this district over Trump in a tight race in the 2020 election, the district went decisively for the Republican candidate in each of the prior four elections. The district is 84% white with a median income of $43,375 and unemployment at 11%.

While the district leans conservative, there is some openness to the idea that climate change is human caused (54%) and many think it can harm future generations (67%). These constituents have a high support for investing in renewables (85.62%).

This district can be won to the Ready For 100 cause and they can be galvanized to put pressure on Michael Waltz to support the policy, as there is some concern for the harms of climate change. As there is likely to be a more conservative mindset in the district, we will emphasize the benefits to the economy in messaging that supports the policy. Due to the lower median income and relatively high unemployment, compared (2.9% for the state in 2019), it will be important to highlight how this policy can bring jobs to the U.S. and to the district.

While we can focus on winning support from the slight majority who believe climate change is human caused, we want to root our messaging in ideals of personal freedoms and individual rights, rather than in a message of communal cooperation. Concerns for personal freedoms are likely to be in line with the type of messaging many of Michael Waltz’ constituents are used to hearing, whether they are listening to Fox News or Ron Paul. Many people on the right might associate climate policy with overbearing government control. We want to point out how climate change policy protects individuals’ rights to a healthy environment, as well as individuals who are not yet born. We also want to tie in some climate issues that will be solved through increase use of renewables such as water pollution, which are more tangible to many people. The messaging won’t be important for gaining support for the policy from more liberal constituents, who are likely to vote against Waltz regardless.

